%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Digital Lab Course on Sophomore Year} % Title
    {Ping Pong Battle with FPGA} % Role
    {Hsinchu, Taiwan} % Location
    {Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implement table tennis game with Verilog on XILINX FPGA, IO with PS/2 Keyboard and graphic with VGA. Featuring simple battle AI, cheat mode and smash like real tennis}
        \item {\href{https://www.youtube.com/watch?v=R4cgMN5uRBE}{Demo video link}}, \href{https://github.com/Alfons0329/DLAB_Fall_2016/tree/master/Final\%20project\%20rev2.0\%20with\%20kill\%20and\%20combo}{Source code link}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {ARM STM32 Embedded Lab on Junior Year} % Role
    {AURA RGB Light} % Title
    {Hsinchu, Taiwan} % Location
    {Dec. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item Embedded-like C, and burn into ARM STM32 board to implement a dynamic, fully-customizable RGB ambient light similar to that of gaming keyboards. 
        \item Understanding the embedded ARM system programming, simple circuit, ADC, and PWM signal control.
        \item \href{https://www.youtube.com/watch?v=FdnTKmdjxIc}{Demo video}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Parallel Programming on Senior Year} % Role
    {Gaussian Blur Paralleled Acceleration} % Title
    {Hsinchu, Taiwan} % Location
    {Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item Accelerate the Gaussian Blur with NVIDIA CUDA framework. 935 times faster on GTX1070 vs i5 7500
        \item \href{https://github.com/Alfons0329/Parallel_Programming_Fall_2018/tree/master/Final\%20Project}{GitHub repo}, \href{https://github.com/Alfons0329/Parallel_Programming_Fall_2018/blob/master/Final\%20Project/Team24_Final_Project_Report.pdf}{Report}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Graduation Project in National Chiao Tung University} % Role
    {Multi-Player Cooperative VR Game} % Title
    {Hsinchu, Taiwan} % Location
    {Sep. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item Computer vision-aided multiplayer real-time VR cooperative gaming using Kinect, Unity and VIVE.
        \item Best project award in Graduation Project Competition of National Chiao Tung University
        \item \href{https://www.youtube.com/watch?v=rYiFose7gZU}{Demo video} \href{https://youtu.be/Kfz1KYMKrtU}{, Presentation video}
      \end{cvitems}
    }
\end{cventries}
